---
title: "Big_Creek_script_8_Parentage_No_duplicates_SibshipInfo_BigCreek.Rmd"
author: 'Noé Barthelemy'
date: "23 mars 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Library 

```{r}
library(tidyverse)
library(reticulate)
```



# I) Introduction 

Hello ! 

The goal here is to : 

Use sibship and duplicates information to run Franz again. 
The sibship info has been deduced from Colony results in script 7. 
The duplicates information has been deduced from an identity analysis in script 6. 

# II) Prepare a full-sib input file 

## A) Franz can detect inconsitencies in fullsibs

FRANz tries to detect inconsistencies in the fullsib assignments: if A,B and B,C are fullsibs, then A and C
must be fullsibs, too. Another explanation would be that either A,B or B,C are false positives. FRANz uses
a simple heuristic here: if it is unlikely that A and C are fullsibs and either A,B or B,C are close to the p-
Value cutoff, then it marks A,B (or B,C, respectively) as false positive. Otherwise FRANz marks A,C as
fullsib (these are the "indirect" fullsibs in siblings.txt).

## B) Who are the certified siblings ?

# CHECK HERE NOE : halfsibin ?

Let's use the multigenerational full siblings,even if in some sibling groups we may have half sibs. 

You can use -halfsibin as an alternative, if you obtain dodgy results (I tested and it is bad, it decreases a lot the confidence we have in assignments, without generating new ones).

The sibs are here: 

"UBC_run1_SibSize_META_Allfish"  
> As created in script 7 section E)    (subject to change)

## C) What format is Fran requiring ? 

Known fullsib relationships are defined with --fullsibin.

Example:
1
3
Bart
Lisa
Maggie

The first line is the number of fullsib or fullsib/halfsib groups, the 3 is the number of fullsibs in the first
group and the following 3 lines contain the ids of the individuals as in the pedigree infile.

## D) Filter Prob(Inc.) > 0.90 in fullsib file 

Basically the lower Prob(Inc.) the higher the probability that siblings can be split in two different families. 
Given that Franz is going to take the fullsibs input file as the exact truth, we should be cautious!

Thus, we will filter sibgroups with a Prob(Inc.) > 0.9 
(No need to filter for 0.99 I think (15 APril 2020))

```{r}
Filtered_Fullsibs <- UBC_run1_SibSize_META_Allfish %>% 
  filter(., `Prob(Inc.)` >= 0.9) %>% 
  group_by(., FullSibshipIndex) %>% 
  mutate(., Sibship_minYear = min(Coll_year)) %>% 
  ungroup()

nrow(UBC_run1_SibSize_META_Allfish)
nrow(Filtered_Fullsibs)
``` 


## E) Let's convert our fullsib file 

```{r}
head(Filtered_Fullsibs)
```
For the first line of the file, we need the numer of sibgroups
```{r}
Filtered_Fullsibs %>% 
  distinct(., FullSibshipIndex) %>% 
  nrow()
```

### 1) Prepare files for python script

Now we need the sibgroup size and the individual ID's
```{r}
ID_and_Sibsize <- Filtered_Fullsibs %>%
  ungroup() %>% 
  select(., c(FullSibshipIndex, Sibsize, Sibship_Member))

FullSibshipIndexes <- Filtered_Fullsibs %>%
  ungroup() %>% 
  select(., FullSibshipIndex) %>% 
  distinct()
 
```
 
```{r}
write_csv(ID_and_Sibsize, path = 'C:/Users/noeba/Desktop/FRANZ_stuff/Duplicates_ID_and_Sibsize.csv' ) 
write_csv(FullSibshipIndexes, path = 'C:/Users/noeba/Desktop/FRANZ_stuff/FullSibshipIndexes.csv' ) 
```
 
### 2) We need to set up python in Rstudio

Check where it is and Run this ! 
```{r}
Sys.which("python")
use_python("C:/Users/noeba/AppData/Local/r-miniconda/envs/r-reticulate/python.exe")
```


### 3) Try with Python

This didn't work, unfortunately !!

Prepare python to be used

```{r}
#remotes::install_github("rstudio/reticulate")
#py_install("pandas")
library(reticulate)
#install_miniconda()
```


```{python}
## Prepare the loop

# Iterate each line
import re
myfilename = 'C:/Users/noeba/Desktop/FRANZ_stuff/Duplicates_ID_and_Sibsize.csv'
new_file = []
Result_file = 'C:/Users/noeba/Desktop/FRANZ_stuff/FranzSibgroups_input.txt'


with open(myfilename, 'r') as maindata:
   # Read the file contents and generate a list with each line
   lines_to_dealwith = maindata.readlines()

groups = {}

for line in lines_to_dealwith:

    Sibgroup_this_line = re.search('([0-9]{1,3}),[0-9]{1,3},[0-9]{1,2},SH_[0-9]+', line) 
    Sibsize_this_line = re.search('[0-9]{1,3},([0-9]{1,2}),SH_[0-9]+', line)    # i.e capture YOY_sibsize_AllYears 
    Member_this_line = re.search('[0-9]{1,3},[0-9]{1,2},(SH_[0-9]+)', line)    # i.e capture Sibship_Member 
    
    if(Sibgroup_this_line not in groups) :               # Changé le ! for not in 
        groups[Sibgroup_this_line] = []
    groups[Sibgroup_this_line].append(Member_this_line)  ## ajouté un s a group au début
    
new_file.append(str(len(groups)))
    
for group in groups:
    new_file.append(str(len(group)))
    
    for member in group:
        new_file.append(member)
        
print(new_file)
#with open(Result_file, 'w') as result:
#  result.writelines(new_file)
```



### 4) Javascript alternative 

Glen wrote me a script to convert automatically to Franz format. 


For that you only need:

1) the input 

Was created just earlier: C:/Users/noeba/Desktop/FRANZ_stuff/Duplicates_ID_and_Sibsize.csv
In format : FullsibshipIndex , sibsize , Sibship_member

2) Install node.js if not done already 

3) Launch a command prompt and navigate to folder containing input AND script

file:///C:/Users/noeba/Desktop/FRANZ_stuff/Sibgroups_for_Franz_script.js

4) run $ node Sibgroups_for_Franz_script.js


# III) Use the clone info ! 

The table "MetagenoALLYEARS_readytotransform2" is created in script 1 before the first Franz run.
We will use it, filter the duplicates and run Franz again! 
The duplicates to remove are in "Duplicates_to_remove_CERVUS".

```{r}
nrow(Duplicates_to_remove_CERVUS)
nrow(MetagenoALLYEARS_readytotransform2)
```

## A) Remove duplicates
```{r}
New_Franz_input_2transform_noDups <- MetagenoALLYEARS_readytotransform2 %>% 
  filter(., !Sample_ID %in% Duplicates_to_remove_CERVUS$Mate_to_remove )
```

```{r}
nrow(New_Franz_input_2transform_noDups)
```
## B) Remove extra metadata
```{r}
New_Franz_input_Ready2transform_noDups <- New_Franz_input_2transform_noDups %>% 
  select(., - c(Coll_year, Pop, WATER_NAME, NMFS_DNA_ID))  
head(New_Franz_input_Ready2transform_noDups)
```

## C) Write file to transform
We will now write the csv file.
```{r}
write_csv(New_Franz_input_Ready2transform_noDups, path = 'C:/Users/noeba/Desktop/FRANZ_stuff/To_transform/New_Franz_input_Ready2transform_noDups.csv' ) 
```

 
## D) Transformation: Follow the steps

1) Please go in the csv file and replace all 'NA' by '?' 

2) Then transform the input thanks to FRANz website tool:  
http://www.bioinf.uni-leipzig.de/Software/FRANz/CSV_Import.html 

3) Then pick the transformed 'file' made by the website with ctrl+A and copy it into the txt file of the transformed folder. 
** (Or in any folder you want, just take one)

 Warning: If you relaunch FRANz it will replace the files each time :)


The transformed file is :   file:///C:/Users/noeba/Desktop/FRANZ_stuff/Transformed/New_Franz_input_transformed_noDups.csv


# IV) Run Franz

The manual is here : https://www.bioinf.uni-leipzig.de/Software/FRANz/FRANz2.pdf
 
## A) Estimate Nmax 

Whats is the maximum number of daddys in our 1995 fish dataset (i.e run 7 to 12).
 
```{r}

FullMeta_V4 %>% 
 filter(., !Sample_ID %in% Duplicates_to_remove_CERVUS$Mate_to_remove ) %>% 
 filter(., Coll_year != 2017) %>% 
  count(., Sex)
 
# So this counting is simplistic but we can go for --Nmax of xxx for now.

```
```{r}
FullMeta_V4 %>% 
 filter(., !Sample_ID %in% Duplicates_to_remove_CERVUS$Mate_to_remove ) %>% 
   filter(., LENGTH >= 150) %>% 
  filter(., Coll_year != 2017) %>% 
  count(., Sex)
```
```{r}
FullMeta_V4 %>% 
 filter(., !Sample_ID %in% Duplicates_to_remove_CERVUS$Mate_to_remove ) %>% 
   filter(., LENGTH < 150) %>% 
  filter(., Coll_year != 2017) %>% 
  count(., Sex)
```
 
 
## B) Error rate 

Here we use 0.001 as an error rate since Diana used that before. Should be fine. 

## C) Input files 

1: The sibgroups file : file:///C:/Users/noeba/Desktop/FRANZ_stuff/FranzSibgroups_input.txt
2: The transformed genotypes file : New_Franz_input_transformed_noDups.csv 

## D) Other options 

--mintyped 115
--hwetestout HWE_test.txt
--maxdepth 8
--Nmax 2000
--n 1556           (i.e 822 males + 734 females in dataset, ruling out year 2017)       
> n here is the sum of candidate males and candidates females in our dataset. 
 OPTIONAL: --maxmismatching 1,2 to rule out bad assignments (reajust threshold based on data visualisation)

## E) Final command line 

> Navigate to file:///C:/Users/noeba/Desktop/FRANZ_stuff/
> Run the following line: 

FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --n 1556 --fullsibin FranzSibgroups_input.txt --Nmax 2000 --maxdepth 8  Transformed/New_Franz_input_transformed_noDups.txt 

> OR with "halfsibin" instead of fullsibin : BAD BAD BAD !!! 

FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --n 1556 --Nmax 2000 --maxdepth 8 --halfsibin FranzSibgroups_input.txt Transformed/New_Franz_input_transformed_noDups.txt 
 
> Then the results arrive in the folder where the analysed files was.
> Move ALL the files of that folder into a dedicated result folder.

# V) Post-Franz 
 
 I moved the results manually to : BigCreek_NoDuplicates_Sibship_info_25march2020 
                                   BigCreek_NoDuplicates_Sibship_info_08April2020
                                   BigCreek_NoDuplicates_HALFSibship_info_10April2020
                                   BigCreek_NoDuplicates_Sibship_info_0.9sibshipFiltering_15April2020
                                   
 We are going to give this run a short nickname : "nicerun"
 
## A) Read the parentage file 

This is one of FRANz outputs
Again, change Metageno2017 by the name of the new result folder. 
    (In the object AND in the path!)

>>> WARNING !!! HERE CHECK WHICH RUN YOU WANT !

BigCreek_NoDuplicates_Sibship_info_25march2020 = With this line: 
FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --Nmax 957 --fullsibin FranzSibgroups_input.txt Transformed/New_Franz_input_transformed_noDups.txt 

BigCreek_NoDuplicates_Sibship_info_08April2020 = With this line: 
FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --n 1556 --Nmax 2000 --maxdepth 8 --fullsibin FranzSibgroups_input.txt Transformed/New_Franz_input_transformed_noDups.txt 
> i.e here we added maxdepth 8, changed Nmax and addedd --n , the number of SAMPLED candidates.

BigCreek_NoDuplicates_HALFSibship_info_10April2020 = With this line: 
FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --n 1556 --Nmax 2000 --maxdepth 8 --halfsibin FranzSibgroups_input.txt Transformed/New_Franz_input_transformed_noDups.txt 
> i.e we just changed --fullsibin to --halfsibin (i.e we don't know if they are half sibs or fullsibs)

BigCreek_NoDuplicates_Sibship_info_0.9sibshipFiltering_15April2020 = 
FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --n 1556 --Nmax 2000 --maxdepth 8 --fullsibin FranzSibgroups_input.txt Transformed/New_Franz_input_transformed_noDups.txt 
> But with this one sibships were filtered for Prob(Inc.) > 0.9 and not 0.99. 

BigCreek_NoDuplicates_Sibship_info_0.9sibshipFiltering_08June2020 = 
FRANz --mintyped 115 --typingerror 0.001 --hwetestout HWE_test_run2.txt --n 1556 --fullsibin FranzSibgroups_input.txt --Nmax 2000 --maxdepth 8  Transformed/New_Franz_input_transformed_noDups.txt
> I didn't really changed anything, I'm just making sure everything was up to date. 


```{r}
parentage_MetagenoALLYEARS_nicerun <- read_csv("C:/Users/noeba/Desktop/FRANZ_stuff/Results/BigCreek_NoDuplicates_Sibship_info_0.9sibshipFiltering_08June2020/parentage.csv")

nrow(parentage_MetagenoALLYEARS)
```
 
 
## B) Filter the results based on prior probability

We set the limit of Posterioir probability at 0.95.
We set the minimu LOD score for parents at a minimum of 5.

```{r}
# Filter it!
  First_filtered_BigCreek_nicerun <- parentage_MetagenoALLYEARS_nicerun %>% 
  filter(!is.na(`Parent 1`)) %>%       # Parent ONE to keep single pairs into the dataset
  filter(Posterior >= 0.99) %>%      # Set the filter here
  filter(`Pair LOD Parent 1` >= 5 | `Pair LOD Parent 2` >= 5)  %>% 
  mutate(., TRIOorSP = if_else(is.na(`Parent 2`), "Single_Pair", "Trio"))
nrow(First_filtered_BigCreek_nicerun)
```
Run 25 March: 383
Run 08 April: 400
Run 10 April: 136 (Kind of big loss here!)
Run 14 April: 374 (Nice enough!)
Run 08 June : 375  


What % of assignment lost with the 0.95 Posterior and 5 Pair LOD filtering ?
```{r}
Without_NA_Unfiltered_nicerun <- parentage_MetagenoALLYEARS_nicerun %>% 
  filter(!is.na(`Parent 1`)) %>% 
  mutate(., TRIOorSP = if_else(is.na(`Parent 2`), "Single_Pair", "Trio"))
  
100 - (nrow(First_filtered_BigCreek_nicerun) * 100) / nrow(Without_NA_Unfiltered_nicerun) 
```
Run 25 March: 16.00877 % 
Run 08 April: 17.86448 %
Run 10 April: 86.73171 %
Run 14 April: 14.02299 % 
Run 08 June : 14.57859 %


## C) Script 2 - based
 
 Above was almost a copy-paste of script 1, adding sibship info and removing duplicates. 
 Now, we will mimick what was done in script two for the first run. 
 
### 1) Count trios and SP

```{r}
First_filtered_BigCreek_nicerun %>% 
  group_by(., TRIOorSP == "Trio") %>% 
  count()
```


```{r}
First_filtered_BigCreek_nicerun %>% 
  group_by(., TRIOorSP == "Single_Pair") %>% 
  count()
```
Run 25 March: 66 Trios and 317 SP
Run 08 April: 66 Trios and 334 SP
Run 15 April: 64 Trios and 310 SP
Run 08 June: 64 Trios and 311 SP


# REPORT AND THINK ABOUT THIS

So with this run we have 148 trios and 527 single pairs, 
And if we reduce the allowed mismatches to 1 for SP and 2 for Trios we obtain only 122 trios and 370 SP !
If we reallow more mismatches and we give all the sibships as input (and not only the YOY) and if we filter for prior > 0.99 we obtain 66 trios and 317 SP. 
This is slightly less than in the first run (176 trios and 586 SP), but it probably eliminated the false ones.  

# REPORT AND THINK ABOUT THIS


### 2) Enrich the dataset 

We use minimeta_V6, which was created later than script two.

This chunk is juste to have the one column format to compute number of kids per parent.
```{r}

tidy_coast_BicCreek_USEFUL_nicerun <- tidy_franz(First_filtered_BigCreek_nicerun) %>% mutate(parent_posterior = round(parent_posterior,2))
head(tidy_coast_BicCreek_USEFUL_nicerun)

# Now we use the dataset transformed by tidyfranz.
# Now we would like to join the info to the regular format dataset.

# We can easily get how many kids a parent had with that dataset.

tidy_coast_BicCreek_USEFUL_totkidperfish_nicerun <- tidy_coast_BicCreek_USEFUL_nicerun %>% 
  group_by(., parent) %>% 
  add_count() %>% 
  filter(., !is.na(parent)) %>% 
  rename(., Number_of_kids_per_parent = n) %>% 
  ungroup() 
# This is a nice file, let join it with our metadata

Numkids_per_parent_nicerun <- tidy_coast_BicCreek_USEFUL_totkidperfish_nicerun %>% 
  distinct(., parent, .keep_all = T) %>% 
  select(., c(parent, Number_of_kids_per_parent))

```

Now just prepare the metadata 
```{r}
Minimeta_for_nicerun <- Minimeta_V6 %>% 
  rename(., parent = "Sample_ID") %>% 
  left_join(., Numkids_per_parent_nicerun, by = "parent")  
```

#### a) For parent 1 

```{r}
Minimeta_for_nicerun_P1_beta <- Minimeta_for_nicerun %>% 
  rename(., parent_1 = "parent") 
colnames(Minimeta_for_nicerun_P1_beta) <- paste(colnames(Minimeta_for_nicerun_P1_beta), "_parent_1", sep = "")
Minimeta_for_nicerun_P1 <- Minimeta_for_nicerun_P1_beta %>% 
  rename(., parent_1 = "parent_1_parent_1") %>%
  select(.,  -c(Population_parent_1, Indiv_parent_1, AGE_parent_1))
  
```

#### b) For parent 2

```{r}
Minimeta_for_nicerun_P2_beta <- Minimeta_for_nicerun %>% 
  rename(., parent_2 = "parent") 
colnames(Minimeta_for_nicerun_P2_beta) <- paste(colnames(Minimeta_for_nicerun_P2_beta), "_parent_2", sep = "")
Minimeta_for_nicerun_P2 <- Minimeta_for_nicerun_P2_beta %>% 
  rename(., parent_2 = "parent_2_parent_2") %>%
  select(.,  -c(Population_parent_2, Indiv_parent_2, AGE_parent_2))
  
```

#### c) For kid

```{r}
Minimeta_for_nicerun_kid <- Minimeta_for_nicerun %>% 
  rename(., kid = "parent") 
colnames(Minimeta_for_nicerun_kid) <- paste(colnames(Minimeta_for_nicerun_kid), "_kid", sep = "")
Minimeta_for_nicerun_kid <- Minimeta_for_nicerun_kid %>% 
  rename(., kid = "kid_kid") %>%
  select(.,  -c(Population_kid, Indiv_kid, AGE_kid, Number_of_kids_per_parent_kid))
  
```
 
Now use those mini datasets to enrich our parentage dataset. 
```{r}

Enriched_nicerun <- First_filtered_BigCreek_nicerun %>% 
  rename(., kid = "Offspring") %>%        # First rename some variables 
  rename(., parent_1 = "Parent 1") %>% 
  rename(., parent_2 = "Parent 2") %>% 
  left_join(., Minimeta_for_nicerun_P1, by = "parent_1" ) %>% 
  left_join(., Minimeta_for_nicerun_P2, by = "parent_2" ) %>% 
  left_join(., Minimeta_for_nicerun_kid, by = "kid" ) 

nrow(Enriched_nicerun)
```


Add "mom" and "dad"
Add family size, with and without Single pairs 
Add mom and dad size and Omy5 


```{r}

Enriched_nicerun_V2 <- Enriched_nicerun %>% 
  mutate(., Mom = ifelse(Sex_parent_1 == "F", parent_1, parent_2 )) %>% 
  mutate(., Dad = ifelse(Sex_parent_1 == "M", parent_1, parent_2 )) %>% 
  group_by(., Mom, Dad, Coll_year_kid) %>%               # Compute family size including SP. 
                                                         # It sucks if it is trios !
  add_count() %>% 
  mutate(FamilySize_SP = ifelse( TRIOorSP == "Single_Pair", n, NA)) %>% 
  select(., - c(n)) %>% 
  ungroup() %>% 
  group_by(., Mom, Dad, TRIOorSP) %>%               # Compute family size EXCLUDING SP
  add_count() %>% 
  mutate(FamilySize_TriosOnly = ifelse( TRIOorSP == "Trio", n, NA)) %>% 
  select(., - c(n)) %>% 
  ungroup()  %>% 
  # If SINGLE - PAIR the family size is per YEAR, so we don't inflate the family sizes ! 
  mutate(.,  FamilySize_SPtrio = ifelse(is.na(FamilySize_SP), FamilySize_TriosOnly, FamilySize_SP ) ) %>% 
  mutate(., Momsize = if_else(condition = Sex_parent_1 == "F", true = LENGTH_parent_1, false =  LENGTH_parent_2)) %>% 
  mutate(., Dadsize = if_else(condition = Sex_parent_1 == "M", true = LENGTH_parent_1, false =  LENGTH_parent_2)) %>%       
  mutate(., MomYear = if_else(condition = Sex_parent_1 == "F", true = Coll_year_parent_1, false =  Coll_year_parent_2)) %>% 
  mutate(., DadYear = if_else(condition = Sex_parent_1 == "M", true = Coll_year_parent_1, false =  Coll_year_parent_2)) %>% 
  mutate(., MomOmy5 = if_else(condition = Sex_parent_1 == "F", true = hapstr_parent_1 , false =  hapstr_parent_2)) %>% 
  mutate(., DadOmy5 = if_else(condition = Sex_parent_1 == "M", true = hapstr_parent_1, false =  hapstr_parent_2)) %>% 
  # Create a column to know number of kids per mom
  mutate(., Number_of_kids_Mom = if_else(condition = Sex_parent_1 == "F", true = Number_of_kids_per_parent_parent_1, false =  Number_of_kids_per_parent_parent_2)) %>%
  mutate(., Number_of_kids_Dad = if_else(condition = Sex_parent_1 == "M", true = Number_of_kids_per_parent_parent_1, false =  Number_of_kids_per_parent_parent_2)) 

```

## D) Script 3 - based 

Now that we have enriched the dataset, we will copy the next script for this new run. 
However, the script 3 was done for Omy5 and we already have this information here ! 
So we will just do a couple of things: 

### 1) Compute a "family type"

```{r}
Enriched_nicerun_V3 <- Enriched_nicerun_V2 %>% 
  group_by(., Mom, Dad ) %>% 
  mutate(., Family_OmyType = if_else(hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "AAAA", "Anadromous", if_else(hapstr_parent_1 == "RRRR" & hapstr_parent_2 == "RRRR", "Resident", if_else( hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "RRRR" | hapstr_parent_1 == "RRRR" & hapstr_parent_2 == "AAAA" | hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "HHHH" | hapstr_parent_1 == "RRRR" & hapstr_parent_2 == "HHHH" | hapstr_parent_1 == "HHHH" & hapstr_parent_2 == "HHHH" | hapstr_parent_1 == "HHHH" & hapstr_parent_2 == "AAAA" | hapstr_parent_1 == "HHHH" & hapstr_parent_2 == "RRRR" , "Mixed", if_else(is.na(hapstr_parent_1) == T | is.na(hapstr_parent_2) == T, "Unknown", "Unknown", missing = "Unknown"))))) %>% 
  ungroup()

Enriched_nicerun_V3$Family_OmyType <- Enriched_nicerun_V3$Family_OmyType %>% 
  replace_na("Unknown")

```

### 2) Check Omy5 incompatibilities within families.  

We follow this rule : 

Parent 1 	Parent 2 	kid 	STATUS
A	        R	        A     Incompatible
H	        R	        A	    Incompatible
R	        R	        A	    Incompatible
A	        R	        R	    Incompatible
A	        H	        R	    Incompatible
A	        A	        R	    Incompatible
A	        A	        H	    Incompatible
R	        R	        H	    Incompatible
A	        H	        A	    OK
A	        A	        A	    OK
H	        H	        A	    OK
H	        R	        R	    OK
H	        H	        R	    OK
R	        R	        R	    OK
A	        R	        H	    OK
A	        H	        H	    OK
H	        R	        H	    OK
H	        H	        H	    OK

Below we keep only some columns for clarity.
Also, we remove the Family_OmyType that are unknown, 
because we cannot determine incompatibilities in those !

Then we compute an "Omy5_compatibility" based on the table above. 
```{r}

Enriched_nicerun_Omy5_incompatibilities <- Enriched_nicerun_V3 %>% 
  select(., parent_1, parent_2, kid,Mismatches, TRIOorSP, hapstr_parent_1, hapstr_parent_2 , hapstr_kid, FamilySize_TriosOnly, Family_OmyType ) %>% 
  filter(., !Family_OmyType == "Unknown") %>% 
  group_by(., parent_1, parent_2, kid) %>% 
  mutate(., Omy5_compatibility = if_else( condition = hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "RRRR" & hapstr_kid == "AAAA" | hapstr_parent_1 == "HHHH" & hapstr_parent_2 == "RRRR" & hapstr_kid == "AAAA" | hapstr_parent_1 == "RRRR" & hapstr_parent_2 == "RRRR" & hapstr_kid == "AAAA" | hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "RRRR" & hapstr_kid == "RRRR" | hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "HHHH" & hapstr_kid == "RRRR" | hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "AAAA" & hapstr_kid == "RRRR" | hapstr_parent_1 == "AAAA" & hapstr_parent_2 == "AAAA" & hapstr_kid == "HHHH" | hapstr_parent_1 == "RRRR" & hapstr_parent_2 == "RRRR" & hapstr_kid == "HHHH", true = "Incompatible_haptstr", false = "compatible_hapstr")) %>% ungroup()

Enriched_nicerun_Omy5_incompatibilities %>% count(., Omy5_compatibility == "Incompatible_haptstr")
```

NO OMY5 INCOMPATIBILITIES ! :D 


## E) Script 4 - based 
 
This script 4 was starting some analysis, so we will repeat them here. 

### 1) Sex ratio 1809 dataset
 
 This is the sex ratio in the total dataset, with the 1809 fish. 
 
```{r}

Sexratio_total <- Minimeta_V8_noDup %>%
  group_by(., Sex) %>% 
  add_count() %>% 
  ungroup()

Numfemales <- Sexratio_total %>% 
  filter(., Sex == "F") %>%
  select(., n)
 numf = Numfemales[1,1] / nrow(MetaALLYEARS)
 numm = (nrow(MetaALLYEARS) - Numfemales[1,1]) / nrow(MetaALLYEARS)
 
numf
numm
# Totalsexratio(F:M) for the complete dataset (rounded) = 0.458 Females : 0.542 Males
```

Run 08 June: 0.4270677 (F) 0.5729323 (M)

 
### 2) Sex ratio in parentage results 

#### a) In parents 


Parents without duplicates, i.e each parent, regardless of the number of breeding relationship (trio/SP) he is part of, is present only once in the count.

```{r} 

Num_moms <- Enriched_nicerun_V3 %>%
  ungroup() %>% 
  select(., Mom) %>% 
  filter(., !is.na(Mom)) %>% 
  distinct(., Mom)

Num_dads <- Enriched_nicerun_V3 %>%
  ungroup() %>% 
  select(., Dad) %>% 
  filter(., !is.na(Dad)) %>% 
  distinct(., Dad)

totparents <- nrow(Num_moms) + nrow(Num_dads) 
nrow(Num_moms) / totparents
nrow(Num_dads) / totparents

# Without the duplicates, we have a sexratio(F:M) of (rounded) : 0.46 F:M 0.54
```
We have a sexratio (F:M) of (rounded) : Females : 0.52
                                        Males   : 0.48

Run 25 March : 
When we give all the sibship info with nor restriction on mismatches: 
We have a sexratio (F:M) of (rounded) : Females : 0.39
                                        Males   : 0.61
 

Run 08 April : 
When we give all the sibship info with nor restriction on mismatches: 
We have a sexratio (F:M) of (rounded) : Females : 0.42
                                        Males   : 0.58
                  
Run 15 April : 
When we give all the sibship info with nor restriction on mismatches: 
We have a sexratio (F:M) of (rounded) : Females : 0.42
                                        Males   : 0.58  
                                        
Run 08 June : 
When we give all the sibship info with nor restriction on mismatches: 
We have a sexratio (F:M) of (rounded) : Females : 0.4020619
                                        Males   : 0.5979381

Up to date in 16/06/2020 : 0.3917526 / 0.6082474
                                        
                                        
#### b) In kids 

```{r}
Sexratio_postparentage_nicerun <- Enriched_nicerun_V3 %>%
  group_by(., Sex_kid) %>% 
  add_count() 

Numfemales_kid_nicerun <- Sexratio_postparentage_nicerun %>% 
  filter(., Sex_kid == "F") %>%  
  select(., n) 

Nummales_kid_nicerun <- Sexratio_postparentage_nicerun %>% 
  filter(., Sex_kid == "M") %>%  
  select(., n) 

 numf_kid_nicerun = Numfemales_kid_nicerun[1,2] / nrow(Enriched_nicerun_V3)
 numm_kid_nicerun = Nummales_kid_nicerun[1,2] / nrow(Enriched_nicerun_V3)
 
numf_kid_nicerun
numm_kid_nicerun
numf_kid_nicerun + numm_kid_nicerun
 
```

Total sexratio (proportions F:M) of kids (rounded) =  Females : 0.51
                                                      Males   : 0.49
  
When we give all the sibship info with nor restriction on mismatches: 
We have a sexratio (F:M) of (rounded) : Females : 0.465
                                        Males   : 0.535
  

#### c) Annual sex ratio in kids 

```{r}
Sex_kids_per_year_nicerun <- Enriched_nicerun_V3 %>% 
  ungroup() %>% 
  select(., Coll_year_kid, kid, Sex_kid) %>% 
  group_by(., Coll_year_kid, Sex_kid) %>% 
  add_count() %>% 
  distinct(., Coll_year_kid, Sex_kid, n) %>% 
  spread(., Sex_kid,  n) %>% 
  rename(., Female = "F", Male = "M") %>% 
  mutate(., Sex_R_proportions_Females = Female/(Female+Male)) %>% 
  ungroup() %>% 
  mutate(., NumKids_this_Years = Female + Male)
```

Let's plot that ?

```{r}
library(ggplot2)

ggplot(Sex_kids_per_year_nicerun) +
 aes(x = Coll_year_kid, y = Sex_R_proportions_Females, colour = NumKids_this_Years) +
 geom_boxplot(fill = "#0c4c8a") +
 scale_color_distiller(palette = "Spectral") +
 labs(x = "Collection year", y = "Proportion of females in kids", color = "Number of kids this year") +
 theme_minimal()
```


 
 
 
# THE END 

You can go to script 9 where we will link the new parentage data with the sibship data. 
 
 
 
 
 
 
 
 
 
### Modified version
 
Below, when YOY_fullsibs were used (rather than the whole dataset) 
 
 ## D) Filter Prob(Inc.) > 0.99 in fullsib file 

Basically the lower Prob(Inc.) the higher the probability that siblings can be split in two different families. 
Given that Franz is going to take the fullsibs input file as the exact truth, we should be cautious!

Thus, we will filter sibgroups with a Prob(Inc.) > 0.99

Filtered_YOY_Fullsibs <- UBC_run1_SibSize_META_Result2_YOYs %>% 
  filter(., `Prob(Inc.)` >= 0.99)

head(UBC_run1_SibSize_META_Allfish)




## E) Let's convert our fullsib file 


For the first line of the file, we need the numer of sibgroups

Filtered_YOY_Fullsibs %>% 
  distinct(., FullSibshipIndex) %>% 
  nrow()


### 1) Prepare files for python script

Now we need the sibgroup size and the individual ID's

ID_and_Sibsize <- Filtered_YOY_Fullsibs %>%
  ungroup() %>% 
  select(., c(FullSibshipIndex, YOY_sibsize_AllYears, Sibship_Member))

FullSibshipIndexes <- Filtered_YOY_Fullsibs %>%
  ungroup() %>% 
  select(., FullSibshipIndex) %>% 
  distinct()
 

 
 
 
 
 
# BONUS : Try CKMRsim instead of FRANz 

Ya ce script de Neil qui peut aider: 
Neil_power_analysis_example_chinook.Rmd (Dans MicrohapSteelhead project)

Va la pour voir ce que Diana as fait : 
D:\Nonopov_travail\Santa_Cruz_internship\New stage\Noe\MicrohapsSteelheadProject\R_MiStPr\nsf-rockfish-parentage












 
 
 
 
 