---
title: "Script_5_Can_parents_be_confounded_with_offsprings"
author: 'Noé Barthelemy'
date: "13 juin 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Aim of the script

The aim of this script is to check if by doing a soup of fish (putting all the fish genotypes in FRANz without specifying any age), old big fish can be assigned as parents of young small fish.


### Important: This script need to run first the "Big_creek_genotypes_script_1.rmd" script first, and the "Big_creek_genotypes_script_2.rmd"


## Find obvious mistakes first

Although, I can also try to find obvious mistakes in my dataset, eg. a fish caught in 2013 as a YOY and assigned as parent of a big fish from 2010 ! 

```{r}
# Select the variables of interest

Impostor_kids_V1 <- Parentage_meta_V4 %>% 
  select(., kid, parent_1, parent_2, Coll_year_kid, REPORTED_LIFE_STAGE_kid, LENGTH_kid, Coll_year_parent_1, REPORTED_LIFE_STAGE_parent_1, LENGTH_parent_1, Coll_year_parent_2, REPORTED_LIFE_STAGE_parent_2, LENGTH_parent_2, TRIOorSP)
head(Impostor_kids_V1)

# Filter the kids collected before their supposed parents

Impostor_kids_V2 <- Impostor_kids_V1 %>% 
  filter(., Coll_year_kid <= Coll_year_parent_1)


head(Impostor_kids_V2)


```


### Now let's create the fake dataset: 
# Strategy

What I can do is go back to FRANz and do a mini test: Take ones that you are sure to not be offsprings 
(like big fish from 2010, 2011, 2012) in a dataset, small fish that you know they can't be parents of those big older guys, ARTIFICIALLY define the big as youngs in FRANz and the young as old ! 

*** We start with the dataset "MetagenoALLYEARS_readytotransform3" created in script 1. 
--> But we do the selection with the original metageno dataset, it's more complete.


```{r}
# The big old parents that are going to be designated as offsprings. 
Big_fish <- MetagenoALLYEARS %>% 
  filter(., LENGTH >= 100) %>% 
  filter(., Coll_year <= 2012)
  
# The young small offsprings that we are going to use for the fake parental pool!
# Notice that we separate the datasets from one year (2012 to 2013) to avoid tricky overlappings that we couldn't say if they are true or fake! 

Small_fish <- MetagenoALLYEARS %>% 
  filter(., !LENGTH >= 100) %>% 
  filter(., !Coll_year <= 2013)
  
Fake_OldKids_Youngparents_v1 <-  MetagenoALLYEARS_readytotransform3 %>% 
  mutate(., age = if_else(Sample_ID %in% Big_fish$Sample_ID, "2010", if_else(Sample_ID %in% Small_fish$Sample_ID, "2000", "Discard"))) %>% 
  filter(., !age == "Discard") %>% 
  select(., age, everything()) %>% 
  select(., Sample_ID, everything())
  

# Just to check we discarded the right fish ! 
  discardedfish <- Fake_OldKids_Youngparents_v1 %>% 
    filter(., age == "Discard")
  Metadiscardedfish <- MetagenoALLYEARS %>% 
    filter(., Sample_ID %in% discardedfish$Sample_ID)  

## Finally, whats is the Nmax here ? 
  Nmaxfortest <- Fake_OldKids_Youngparents_v1 %>% 
    filter(., age == 2000 & Sex == "M")
  nrow(Nmaxfortest)
  
  head(Nmaxfortest)
  head(MetagenoALLYEARS_readytotransform2)
  head(Fake_OldKids_Youngparents_v1)
  nrow(Fake_OldKids_Youngparents_v1)
```


We will now write the csv file.
```{r}
write_csv(Fake_OldKids_Youngparents_v1, path = 'C:/Users/noeba/Desktop/FRANZ_stuff/Test_Oldkids_YoungParents/To_transform/Fake_OldKids_Youngparents_v1.csv' )

```

###### AFTER THE CREATION OF THE CSV FILE FOR FRANZ:

 IMPORTANT STEP 
!!! Replace all 'NA' by '?' in the file to transform !! 



Then transform the input thanks to FRANz website tool:  
http://www.bioinf.uni-leipzig.de/Software/FRANz/CSV_Import.html 

** Then pick the transformed 'file' made by the website with ctrl+A and copy it into the txt file of the transformed folder. 
** (Or in any folder you want, just take one)
      
  ###
  ###    But be careful !! 
  ###    If you relaunch FRANz he will replace the files each time :)
  ###
           
## Run Franz

The manual is here : https://www.bioinf.uni-leipzig.de/Software/FRANz/FRANz2.pdf

  THE OPTIONS 
 
 1) --mintyped 115            :  This will not change
 2) --typingerror 0.005       :  Same
 3) --hwetestout HWE_test.txt :  To have the HWE test
 4) --Nmax XXX                :  We saw just above that the Nmax here is 309. 
 5) --fullsibtest             :  To detect fullsibs
 6) --fullsibparental         :  Same, in the parental pool.
 7) --malerepro 15:200        :  Because you don't want the fish of age 10 (fake offsprings) to be assigned as                                         parents. 
 8) --femrepro 15:200         :  Same. 
 
 Then here is the command line on windows 10 for running FRANz:


           FRANz --mintyped 115 --typingerror 0.005 --hwetestout HWE_test.txt --fullsibtest --fullsibparental --malerepro 5:200 --femrepro 5:200 --Nmax 309 Fake_OldKids_Youngparents_v1_Transformed_21082019.txt

 So I inputed the femrepro and malerepro options to 5:200 so that the fish of age 10 (fake offsprings) cannot be assigned as parents. 

Then the results arrive in the folder where the analysed files was.
Move ALL the files of that folder into a dedicated result folder.

#### Read the parentage file of the test 

This is one of FRANz outputs
Again, change Metageno2017 by the name of the new result folder. 
    (In the object AND in the path!)

```{r}
FakeRun_test_results <- read_csv("C:/Users/noeba/Desktop/FRANZ_stuff/Test_Oldkids_YoungParents/Results/parentage.csv")

head(FakeRun_test_results)
```

 READER: So here we are just trying to see is there was some assignments and why 

```{r}
#Create a minimeta for kids
Minimeta_kids <- Minimeta_V4 
colnames(Minimeta_kids) <- paste(colnames(Minimeta_kids), "_kid", sep = "")
Minimeta_kids <- Minimeta_kids %>% 
  rename(., Sample_ID = "Sample_ID_kid")

Minimeta_Parent1 <- Minimeta_V4 
colnames(Minimeta_Parent1) <- paste(colnames(Minimeta_Parent1), "_parent1", sep = "")
Minimeta_Parent1 <- Minimeta_Parent1 %>% 
  rename(., `Parent 1` = "Sample_ID_parent1")  



FakeRun_test_results_V2 <- FakeRun_test_results %>% 
    filter(., !is.na(`Parent 1`)) %>% 
    mutate(., TRIOorSP = if_else(is.na(`Parent 2`), "Single_Pair", "Trio")) %>% 
    rename(., Sample_ID = "Offspring") %>% 
    left_join(., Minimeta_kids, by ="Sample_ID") %>% 
    rename(., kid = "Sample_ID") %>% 
    left_join(., Minimeta_Parent1, by = "Parent 1") 


    rename(., kid = "Sample_ID") 

View(FakeRun_test_results_V2)

```

CONCLUSION: 

This test resulted in the assignments of 17 single-pairs on a dataset of 795 fish (parents and offsprings). These had a LOD-score going from 9 to 54. Some had mismatches, some not. Only 2 / 17 had a posterior probability of less than 0.95 (which is what we would reject with our actual filters). 
Worth noting that: 
Reassuring
Worrying
No trios were assigned
Many are assigned with a high probability
Giving the age info to FRANz may have produced strong assignments that would have had a much lower probability or would have been rejected by FRANz otherwise. 
The high “statistical power” that we have with our marker is not sufficient to overcome the problem of closely related individuals. 
There are only 17 assignments. 
17 is still too much ! 

# Then we skyped with Devon. 

# So we are Ok about that. 


# Last thing: Check if those 17 pairs can be found in the current parentage dataset! 

Currently, the last dataset is SibsAndParentage_V3 (08 April 2020).

```{r}
Fake17_disappeared <- SibsAndParentage_V3 %>% 
  filter(., kid %in% FakeRun_test_results_V2$kid)

nrow(Fake17_disappeared)
```
Hoho !! So we still find two ! 
But wait, do they have the same parents? 
```{r}
Fake17_disappeared
```
```{r}
FakeRun_test_results_V2_check <- FakeRun_test_results_V2 %>% 
  filter(.,  kid %in% Fake17_disappeared$kid)
FakeRun_test_results_V2_check
```

So none of them are found ! Now, this doesnt' mean we don't have other problems with our new assignments though !


--------------- END --------------------







