---
title: "Big_creek_Analysis_Script4"
author: 'Noé Barthelemy'
date: "21 juillet 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script follows script 3 and begins with Parentage_meta_Omy_V5

# Library

We go to the library first.
  
```{r,warning=FALSE,message=FALSE}
library(knitr)
library(tidyverse)
library(readxl)
library(esquisse)
```
  
 

# The main analysis 

This is a draft of analysis. It's refined with a better Franz run in script 9. 

# Questions for the Paper: 

We have to: 

  
  1) That is part of the analysis: How defining different groups for parentage affects the results? 
  
  I will continue that after Devon's comments (21/07/2019)
  
      - Define groups of parents and kids troughout the years. 
      - The ones under 80mm FL are juveniles (YOY) : easy.
      - The big-tagged individuals are necessarily adults (>100mm). 

      In the end we didn't do it but its a possibility to do that: 

          - The logic is: 
          YOY individuals from year X should be the offspring of individuals from X-1.
          --> Apply this logic with plenty of small analysis and you should find all the trios and pairs.

          - Then don't forget to compare datasets to check for parents who came and spawned during several years.  

  2) Family structures and stuff
  
  2.1) Check Sex ratio in each dataset too (before parentage and after)
  2.2) Family sizes
  2.3) Effect of drought on family structure ?
  
  !!!!!  TO BE DONE : 
  2.4) Check that there are no full-sibs families ACROSS yoy cohorts. (In next run of FRANz I have to look for full-sibs and then check that among the fratries I don't have different years)



  3) Omy5 analysis
  
  - Check Omy5 HWE the overall population, in residents, in anadromous, in Female, in Males.
  - The big-tagged individuals that are >150mm are RESIDENTS.
  - You should see a bias towards: 
      a) RR genotypes should be residents
      b) AA genotypes should be anadromous (i.e absent in >150mm individuals)
      c) AR genotypes should be biased towards :
          1) Females anadromous
          2) Resident males
  - What is the ditribution of Omy5 genotypes in adults vs youngs ?
    --> Espect a residency effect.
  - Juvenile RR families will be rare and small (and we may find a resident mother), 
    while AR individuals and families will be excessively common.
  - Does Omy5 genotype (i.e anadromous behavior) influence family size?
  - Does Omy5 genotype influence lifetime reproductive success? 
    ** Just for individuals that we see as YOY and don't appear after (i.e dead) **
    ** Maybe mostly resident males ? ** 

Omy5 -- Hypotheses:

 -We will identify many more fathers than mothers among the residents.
    -- this follows from the known female bias in andromy.
    -- sex ratios in various cohorts also interesting to compare.

 Siblings will be spatially clustered by reach within the creek.
    --the Upper Big creek reach is 750m, diveded into 25m shocking sections.

  The most interesting inference will come from comparing distributions of Omy05 genotypes among residents (>150 or 180mm) vs. juveniles, and comparing both with HWE expectations. Omy5 genotypes will reflect sex-dependent dominance of anadomy—Females residents will almost all be RR. Juvenile RR families will be rare and small (and we may find a resident mother), while AR individuals and families will be excessively common.






  4) Do the summary statistics at some point
 
 
 
 
 
                                        LET'S BEGIN !
  
  Let's just plot the number of fish caugth per year, with the sex ratio.
```{r}

FishSex_perYear <- ggplot(data = FullMeta_V4) +
  aes(x = Coll_year, fill = Sex) +
  geom_bar() +
  theme_minimal() 
ggsave("Distribution of fish collection year, showing sex proprtions.png", plot = FishSex_perYear, path = "D:/Nonopov_travail/Santa_Cruz_internship/New stage/Noe/BigCreek project/Results/Plots/")

```
  
  
  
  
  
# I) How defining groups influences the parentage ? 
  
  
  
  I don't remember (20/08/2019) but I may have, in earlier scripts (i.e 1, 2 or 3) checked for Parents-offsprings years incompatibilities. But let's do it again. 
  
```{r}
head(Parentage_meta_Omy_V6)
Parentage_fuckedUp <- Parentage_meta_Omy_V6 %>% 
  select(., c(Momsize, Dadsize, Mom, Dad, DadYear, MomYear, LENGTH_kid, Coll_year_kid, kid))

Parentage_fuckedUp_V2 <- Parentage_fuckedUp %>% 
  mutate(., Size_Incompati = if_else(Momsize <= LENGTH_kid, "Mom2small", if_else(Dadsize <= LENGTH_kid, "Dad2small", "OK" )))


```
  

  
  
# II) Family structures and stuff

## A) Check Sex ratio in each dataset too (before parentage and after)
    
### 1) Sex ratios before analysis (complete dataset)
```{r}
# The complete dataset to take is MetaALLYEARS I think

  # Sex ratio of the 1995 fish 
Sexratio_total <- MetaALLYEARS %>%
  group_by(., Sex) %>% 
  add_count() %>% 
  ungroup()
Numfemales <- Sexratio_total %>% 
  filter(., Sex == "F") %>%
  select(., n)
 numf = Numfemales[1,1] / nrow(MetaALLYEARS)
 numm = (nrow(MetaALLYEARS) - Numfemales[1,1]) / nrow(MetaALLYEARS)
 
numf
numm
# Totalsexratio(F:M) for the complete dataset (rounded) = 0.458 Females : 0.542 Males

  
  # Sex ratio by years

Sexratioyears <- MetaALLYEARS %>%
  group_by(., Coll_year, Sex) %>% 
  add_count() %>% 
  distinct(., Coll_year, Sex, .keep_all = T) %>% 
  select(., c(Coll_year, Sex, n)) %>% 
  spread(., Sex, n) %>% 
  mutate(., Sexratio = F/(M+F))

plot(Sexratioyears$Coll_year, Sexratioyears$Sexratio, xlab = "Years", ylab= "Sex ratio (% females)", main = "Sex ratio per year in 1995 big creek mykiss")


View(Sexratio)
View( )
```


### 2) Sex ratios after analysis (Parentage dataset)
  
For Kids and then for parents (with and without uniques, see below)
  
#### a) Kids
```{r}
# The complete dataset to take is Parentage_meta_Omy_V5 
 
 # Sex ratio of the kiddos
Sexratio_postparentage <- Parentage_meta_Omy_V5 %>%
  group_by(., Sex_kid) %>% 
  add_count() 
Numfemales_kid <- Sexratio_postparentage %>% 
  filter(., Sex_kid == "F") %>%  
  select(., n) 
 numf_kid = Numfemales_kid[1,2] / nrow(Parentage_meta_Omy_V5)
 numm_kid = (nrow(Parentage_meta_Omy_V5) - Numfemales_kid[1,2]) / nrow(Parentage_meta_Omy_V5)
 
numf_kid
numm_kid
# Total sexratio(proportions F:M) of kids (rounded) = 0.496 Females : 0.504 Males


```
#### b) Parents 

  (some duplicates, i.e involved in more than one trio/SP)

```{r}

 # Sex ratio of the parents (i.e even if the parents are common across different trios/single-pairs !!)
 # Note that it should be 50% if their was only propper loyal couples

Num_moms <- Parentage_meta_Omy_V5 %>% 
  select(., Mom) %>% 
  filter(., !is.na(Mom)) 
Num_dads <- Parentage_meta_Omy_V5 %>% 
  select(., Dad) %>% 
  filter(., !is.na(Dad)) 

totparents <- nrow(Num_moms) + nrow(Num_dads) 
nrow(Num_moms) / totparents
nrow(Num_dads) / totparents

# Taking into account the fact that some parents are duplicated here (i.e involved in different trios/SP), we have a   sexratio(F:M) of (rounded) : 0.435 F:M 0.565
```
  
Parents (without duplicates, i.e each parent, regardless of the number of breeding relationship (trio/SP) he is part of, is present only once in the count ! :)

```{r}
 # Sex ratio of the parents
 # Note that it should be 50% if their was only propper loyal couples (lol)

Num_moms <- Parentage_meta_Omy_V5 %>%
  ungroup() %>% 
  select(., Mom) %>% 
  filter(., !is.na(Mom)) %>% 
  distinct(., Mom)
Num_dads <- Parentage_meta_Omy_V5 %>%
  ungroup() %>% 
  select(., Dad) %>% 
  filter(., !is.na(Dad)) %>% 
  distinct(., Dad)

totparents <- nrow(Num_moms) + nrow(Num_dads) 
nrow(Num_moms) / totparents
nrow(Num_dads) / totparents

# Without the duplicates, we have a   sexratio(F:M) of (rounded) : 0.46 F:M 0.54
```

### 3) Sex-ratios of kids per year
    
```{r}
Sex_kids_per_year <- Parentage_meta_Omy_V5 %>% 
  ungroup() %>% 
  select(., Coll_year_kid, kid, Sex_kid) %>% 
  group_by(., Coll_year_kid, Sex_kid) %>% 
  add_count() %>% 
  distinct(., Coll_year_kid, Sex_kid, n) %>% 
  spread(., Sex_kid,  n) %>% 
  rename(., Female = "F", Male = "M") %>% 
  mutate(., Sex_R_proportions_Females = Female/(Female+Male))

FpkidsPeryear <- ggplot(data = Sex_kids_per_year) +
  aes(x = Coll_year_kid, y = Sex_R_proportions_Females) +
  geom_boxplot(fill = "#ef562d") +
  labs(title = "Evolution of proportion of females among kids through time",
    y = "Sex ratio (Proportion of females)") +
  theme_minimal()

ggsave("Evolution of proportion of females among kids through time.png", plot = FpkidsPeryear, path = "D:/Nonopov_travail/Santa_Cruz_internship/New stage/Noe/BigCreek project/Results/Plots/")

head(Sex_kids_per_year)
```


```{r}
### THIS DATASET IS JUST TO CALCULATE THE PROPORTION OF FEMALES AMONG PARENTS THROUGH YEARS ###
Sex_parents_per_year_1 <- Parentage_meta_Omy_V6 %>% 
  ungroup() %>% 
  select(., Coll_year_parent_1, parent_1, sex_1) 

nrow(Sex_parents_per_year_1)

Sex_parents_per_year_2 <- Parentage_meta_Omy_V6 %>% 
  ungroup() %>% 
  select(.,Coll_year_parent_2, parent_2, sex_2) %>% 
  rename(., Coll_year_parent_1 = "Coll_year_parent_2", parent_1 = "parent_2", sex_1 = "sex_2" )

Sex_parents_per_year <- bind_rows(Sex_parents_per_year_1, Sex_parents_per_year_2) %>% 
   filter(., !is.na(parent_1)) 
Sex_parents_per_year <- Sex_parents_per_year %>% 
  unique()

ParentsexR_years <- ggplot(data = Sex_parents_per_year) +
  aes(x = Coll_year_parent_1, fill = sex_1) +
  geom_bar() +
  labs(title = "Sex ratios among parents through years",
    x = "Collection year of parents",
    y = "Count") +
  theme_minimal()

ggsave("Evolution of sex ratio in parents through time.png", plot = ParentsexR_years, path = "D:/Nonopov_travail/Santa_Cruz_internship/New stage/Noe/BigCreek project/Results/Plots/")

View(Parentage_meta_Omy_V6)
```



## B) Family sizes
      
      I think I did calculate the family sizes somewhere !


#### 1) Find some correlations ? 
      
      So what could be interesting ? 
      
   A)   * Family size X Momsize   (Continuous X Continuous)
   B)   * Family size X Dadsize   (Continuous X Continuous)
   C)   * Family size X Collection year      (Continuous X Semi-Continuous)
   D)   * Family size X MomOmy5   (Continuous X Qualitative)
   E)   * Family size X DadOmy5   (Continuous X Qualitative)
      Anything else ?
      
      My idea is to do here an Aikake Criterion thing, to see what is affecting the most the family size.
      
```{r}
head(Parentage_meta_Omy_V6)
View(Parentage_meta_Omy_V6)

Parentage_meta_Omy_V6 <- Parentage_meta_Omy_V5 %>% 
  mutate(., Momsize = if_else(condition = sex_1 == "F", true = LENGTH_parent_1, false =  LENGTH_parent_2)) %>% 
  mutate(., Dadsize = if_else(condition = sex_1 == "M", true = LENGTH_parent_1, false =  LENGTH_parent_2)) %>%       
  mutate(., MomYear = if_else(condition = sex_1 == "F", true = Coll_year_parent_1, false =  Coll_year_parent_2)) %>% 
  mutate(., DadYear = if_else(condition = sex_1 == "M", true = Coll_year_parent_1, false =  Coll_year_parent_2)) %>% 
  mutate(., MomOmy5 = if_else(condition = sex_1 == "F", true = Omy_parent_1 , false =  Omy_parent_2)) %>% 
  mutate(., DadOmy5 = if_else(condition = sex_1 == "M", true = Omy_parent_1, false =  Omy_parent_2))



esquisse::esquisser(Parentage_meta_Omy_V6)

library(ggplot2)

ggplot(Parentage_meta_Omy_V6) +
 aes(x = FamilySize_SPtrio) +
 geom_histogram(bins = 30L, fill = "#0c4c8a") +
 theme_minimal()
head(Parentage_meta_Omy_V6)

```
      
Tentons un AIC sur nos petits modèles ici. 
Ask people if that's good ! 
```{r}
Lm_FS1 <- lm(formula = FamilySize_SPtrio ~ Momsize , data = Parentage_meta_Omy_V6)
Lm_FS2 <- lm(formula = FamilySize_SPtrio ~ Dadsize , data = Parentage_meta_Omy_V6)
Lm_FS3 <- lm(formula = FamilySize_SPtrio ~ as.numeric(MomYear) , data = Parentage_meta_Omy_V6)
Lm_FS4 <- lm(formula = FamilySize_SPtrio ~ as.numeric(DadYear) , data = Parentage_meta_Omy_V6)
Lm_FS5 <- lm(formula = FamilySize_SPtrio ~ MomOmy5 , data = Parentage_meta_Omy_V6)
Lm_FS6 <- lm(formula = FamilySize_SPtrio ~ DadOmy5 , data = Parentage_meta_Omy_V6)

AIC(Lm_FS1, Lm_FS2, Lm_FS3, Lm_FS4, Lm_FS5, Lm_FS6)
# Maybe I should do logistic models for the last two ? 


# Without the single-pairs

Lm_FS1b <- lm(formula = FamilySize_TrioOnly ~ Momsize , data = Parentage_meta_Omy_V6)
Lm_FS2b <- lm(formula = FamilySize_TrioOnly ~ Dadsize , data = Parentage_meta_Omy_V6)
Lm_FS3b <- lm(formula = FamilySize_TrioOnly ~ as.numeric(MomYear) , data = Parentage_meta_Omy_V6)
Lm_FS4b <- lm(formula = FamilySize_TrioOnly ~ as.numeric(DadYear) , data = Parentage_meta_Omy_V6)
Lm_FS5b <- lm(formula = FamilySize_TrioOnly ~ MomOmy5 , data = Parentage_meta_Omy_V6)
Lm_FS6b <- lm(formula = FamilySize_TrioOnly ~ DadOmy5 , data = Parentage_meta_Omy_V6)

AIC(Lm_FS1b, Lm_FS2b, Lm_FS3b, Lm_FS4b, Lm_FS5b, Lm_FS6b)


```
The most explanatory variable seems to be the Mom's size here. 
The second one is when the Mom is caught: But a Pearson test showed that the size and Collection year of the mom are not correlated. 
The Omy5 genotype doesn't explain a lot like this (I would have expected that AAAA females may have larger family sizes and that this would explain a lot, but it doesn't !)
Interestingly, in all the models I tested, values of females explained better the family size than values of males, for the same variable (valid for the Size, the Year of collection, and the Omy5 genotype).
Using the same models but without the Single pairs has a small effect but nothing remarquable.

    Maybe it is still interesting to run some correlation tests: 
```{r}
# Maybe some correlation tests
# 1) Mom size and year of collection
cor.test(x = Parentage_meta_Omy_V6$Momsize, y = as.numeric(Parentage_meta_Omy_V6$MomYear), method = "pearson")
# 2) Mom size and Family size
cor.test(Parentage_meta_Omy_V6$FamilySize_SPtrio, Parentage_meta_Omy_V6$Momsize, method = "p")
# 3) Dad size and Family size
cor.test(Parentage_meta_Omy_V6$FamilySize_SPtrio, Parentage_meta_Omy_V6$Dadsize, method = "p")
# 4) Mom Omy5 genotype and Family size

# 5) Dad Omy5 genotype and Family size

# 6) Family size and loci typed in the kid
cor.test(Parentage_meta_Omy_V6$FamilySize_SPtrio, Parentage_meta_Omy_V6$`Loci Typed`, method = "p")


 CONTINUE THAT LATER  
 CONTINUE THAT LATER 
 CONTINUE THAT LATER 
 CONTINUE THAT LATER 
 CONTINUE THAT LATER 

 esquisse::esquisser()


Subest_parentage_Omy_V6 <- Parentage_meta_Omy_V6 %>% 
  select(., Momsize, Dadsize, FamilySize_SPtrio, FamilySize_TrioOnly, Mismatches, LOD, MomOmy5, DadOmy5, MomYear, DadYear)

glm.fit <- glm(FamilySize_SPtrio ~ MomOmy5 + DadOmy5 , data = Subest_parentage_Omy_V6, family = binomial)

# This shows nothing interesting. 
library(corrplot)
correlations <- cor(Subest_parentage_Omy_V6)
corrplot(correlations, method="circle")

```
    Results of correlation tests on the 28/07/2019: 
    # 1) Mom size and year of collection : Not significant
    # 2) Mom size and Family size        : Highly Significant
    # 3) Dad size and Family size        : Highly Significant
    # 4) Mom Omy5 genotype and Family size : Need to do a glm
    # 5) Dad Omy5 genotype and Family size : Need to do a glm
    # 6) Family size and collection year : TO DO 
    # 7) 
 
 
 
#### 2) Check average family size per sex. 
 
 Attention c'est un peu douteux cette histoire de taille de famille je suis un peu paumé !! 
 
```{r}

Parental_famsize <- Parentage_meta_Omy_V6 %>% 
  filter(., !is.na(FamilySize_TrioOnly))

PaternalFamsize <- Conserv_FamiSize_V3 %>% 
  ungroup() %>% 
  distinct(., Conserv_FamiSize_V3$Dad, .keep_all =  T)
mean(PaternalFamsize$FamilySize_A)

MaternalFamsize <- Conserv_FamiSize_V3 %>% 
  ungroup() %>% 
  distinct(., Conserv_FamiSize_V3$Mom, .keep_all =  T)
mean(MaternalFamsize$FamilySize_A)



head(Parental_famsize)
head(Parentage_meta_Omy_V6)



```
 
 
 
# The end of script 4











